### 2019-04-09 5_evaluation.tex
Update evaluation text.

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs. Some of the slower systems
are omitted from comparisons with more complicated dependence
patterns, as they did not complete in reasonable time 
or reach METG(50\%) even with the largest problem size.

>>>>

The gap between MPI and other systems shrinks as the complexity of the
communication pattern grows, and even reverses as task parallelism is
added in the form of multiple task graphs. Some slower systems
are omitted from comparisons with more complicated dependence
patterns, as the higher overheads of these systems would have required
unreasonably large problem sizes (beyond what can be completed in 6 hours) to reach 50\% efficiency.
